---
title: "Terrorism Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar:
        - { class: "alvaro", icon: "fa-linkedin", href: "https://www.linkedin.com/in/alvaro-mazcu-herreros/", align: right}
        - { class: "miquel", icon: "fa-linkedin", href: "https://www.linkedin.com/in/miquel-marin-colome/", align: right}
    vertical_layout: fill
    includes:
        in_header: "./data/favicon.html" 
  runtime: shiny-prerendered
      
---

<style>

.toolbar {
  visibility: hidden;
}
.navbar {
  background-color:#AB0E1D;
  border-color:black;
  color:white;
}
.navbar-brand {
color:white!important;
}

.navbar-nav {
  background-color:#AB0E1D;
  border-color:black;
}

.navbar-nav li a:hover, .navbar-nav > .active > a {
color: white !important;

background-color:#373737 !important;
}

.chart-title{
  background-color:#373737;
  border-color:#373737;
  color:white;
}

.chart-stage.chart-stage-flex{
  background-color:#373737;
  border-color:#373737;
}

.section.level3.chart-wrapper.chart-wrapper-flex{
  border-color:#373737;
}

ul.nav.nav-tabs{
  background-color:#373737;
  border-color:#373737;
}

.nav.nav-tabs{
  background-color:#373737;
  border-color:#373737;
}

.nav.navbar-nav.navbar-right li a[href$='https://www.linkedin.com/in/alvaro-mazcu-herreros/'] span::before{
  content: "Álvaro Mazcuñán";
}

.nav.navbar-nav.navbar-right li a[href$='https://www.linkedin.com/in/miquel-marin-colome/'] span::before{
  content: "Miquel Marín";
}

.section.sidebar {
  background-color:#373737;
  color:white;
}

body{
  background-color:#373737;
}


</style>


```{r setup, include=FALSE}
setwd(system('pwd', intern = T))
library(flexdashboard)
library(ggplot2)
library(plotly)
library(dplyr)
library(shiny)
library(stringr)
library(jsonlite)
library(knitr)
```

```{r, context="data", include=FALSE}
Sys.setenv("MAPBOX_TOKEN" = 'pk.eyJ1IjoibWF6Y3UiLCJhIjoiY2tpaWlkN29zMDFqaDJ5cWw0Znd4MXJrbyJ9.aHwHbfssypluXdQi1QDRMg') # for Orca
data_1 = read.csv("./data/df.csv")
data_ = read.csv("./data/terrorism.csv")
df_bar = read.csv("./data/df_attacktype.csv")
por_anyo_costes = read.csv("./data/por_anyo_costes.csv")
por_anyo_total = read.csv("./data/por_anyo_total.csv")

geojson <- readLines("./data/countries.geo.json", warn = FALSE) %>%
  paste(collapse = "\n") %>%
  fromJSON(simplifyVector = FALSE)

lista = c('Assassination', 'Armed assault', 'Bombing/explosion', 'Hijacking', 'Hostage taking (barricade incident)', 'Hostage taking (kidnapping)', 'Facility/infraestructure attack', 'Unarmed assault', 'Unknown')
```


Terrorism deaths per country
========================================

### Terrorism deaths per country


```{r, context="server-start"}
fig <- plot_ly()
fig <- fig %>% add_trace(
  type = "choroplethmapbox",
  geojson = geojson,
  locations = data_1$code,
  z=data_1$nkill,
  colorscale="YlOrRd",
  reversescale = T,
  zmin=0,
  zmax=10000,
  marker=list(line = list(
    width = 0),
    opacity=0.5
  )
)
fig <- fig %>% layout(
  mapbox = list(
    style = "dark",
    zoom =3,
    center = list(lon = 0, lat = 0))
)

fig <- fig %>% layout(paper_bgcolor='rgb(25,26,26)')  %>% 
          layout(plot_bgcolor='rgb(25,25,26)')
fig <- fig %>%
  config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

fig

```


Terrorism attacks map
========================================

### Terrorism attacks map

```{r,context="server-start"}


vector = c(1970:2017)


fig <- data_
fig <- fig %>%
  plot_ly(
    lat = ~latitude,
    lon = ~longitude,
    marker = list(color = "#F5CA0F"),
    type = 'scattermapbox',
    text = ~paste('Country: ', country_txt, '<br>Site: ', city, '<br>Deaths: ', nkill, '<br>Wounds: ', nwound, '<br>Date: ', paste(iday, imonth, iyear, sep = '/')),
    hoverinfo = "text", size = I(5))
fig <- fig %>%
  layout(
    mapbox = list(
      style = 'dark',
      zoom =1.5,
      center = list(lon = 0, lat = 0)))

fig <- fig %>% layout(paper_bgcolor='rgb(25,26,26)')  %>% 
          layout(plot_bgcolor='rgb(25,25,26)') %>% config(displayModeBar = FALSE)
fig <- fig %>%
  config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

fig

```



General graphics
=====================================
Inputs {.sidebar}
------------------------------------

```{r}


selectInput('Tipo', label = 'Select attack type: ', choices = lista, selected = '1')

```

Column
-------------------------------------

### Attack type map

```{r}


renderPlotly({
pos = match(input$Tipo, lista)
fig <- subset(data_, data_$attacktype1 == as.character(pos))
fig <- fig %>%
  plot_ly(
    lat = ~latitude,
    lon = ~longitude,
    marker = list(color = "#F5CA0F"),
    type = 'scattermapbox',
    text = ~paste('Site: ', city, '<br>Deaths: ', nkill, '<br>Wounds: ', nwound, '<br>Date: ', paste(iday, imonth, iyear, sep = '/')),
    hoverinfo = "text", size = I(5))
fig <- fig %>%
  layout(
    mapbox = list(
      style = 'dark',
      zoom =1.5,
      center = list(lon = 0, lat = 0)))

fig <- fig %>% layout(paper_bgcolor='rgb(25,26,26)')  %>% 
          layout(plot_bgcolor='rgb(25,25,26)') %>% config(displayModeBar = FALSE)
fig <- fig %>%
  config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

fig
})
```


Column
-------------------------------------

### Most popular attacks per year

```{r, context="server"}

t <- list(
  family = "helvetica",
  size = 12,
  color = 'white')

plot_ly(por_anyo_total, x=~as.numeric(as.character(nattack)), y=~attacktype1, frame = ~iyear, color = I('#FA7214'), showlegend = F, text = ~paste0(attacktype1, ': ',as.numeric(as.character(nattack))), hoverinfo = 'skip', textposition = 'outside', outsidetextfont = list(size=12, color = 'rgb(255,255,255)')) %>% animation_opts(frame = 800, redraw = F, transition = 800) %>% animation_slider(currentvalue = list(prefix = "YEAR ", font = list(color="white"))) %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(visible = F),
    xaxis = list(title = ''))

```

### Number of attacks by economical impact

```{r, context="server"}
plot_ly(por_anyo_costes, x=~as.numeric(as.character(nattack)), y=~costes, frame = ~iyear, color = I('#F53920'), showlegend = F, text = ~paste0(costes, ': ',as.numeric(as.character(nattack))), hoverinfo = 'skip', textposition = 'outside', outsidetextfont = list(size=12, color = 'rgb(255,255,255)')) %>% animation_opts(frame = 800, redraw = F, transition = 800) %>% animation_slider(currentvalue = list(prefix = "YEAR ", font = list(color="white"))) %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(visible = F),
    xaxis = list(title = ''))
```



Per country
=====================================

Inputs {.sidebar}
------------------------------------

```{r}

selectInput('Country', label = 'Select a country: ', choices = str_sort(unique(data_$country_txt)), selected = 'Spain')
```


Column {data-width=750}
-------------------------------------

### Attacks map

```{r}

renderPlotly({
fig <- subset(data_, data_$country_txt == input$Country)
fig <- fig %>%
  plot_ly(
    lat = ~latitude,
    lon = ~longitude,
    marker = list(color = "#F5CA0F"),
    type = 'scattermapbox',
    text = ~paste('Site: ', city, '<br>Deaths: ', nkill, '<br>Wounds: ', nwound, '<br>Date: ', paste(iday, imonth, iyear, sep = '/')),
    hoverinfo = "text", size = I(5))
fig <- fig %>%
  layout(
    mapbox = list(
      style = 'dark',
      zoom =4.15,
      center = list(lon = ~mean(longitude), lat = ~mean(latitude))))

fig <- fig %>% layout(paper_bgcolor='rgb(25,26,26)')  %>% 
          layout(plot_bgcolor='rgb(25,25,26)') %>% config(displayModeBar = FALSE)
fig <- fig %>%
  config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

fig
})
```

Column {data-width=250}
-------------------------------------

### Total deaths

```{r}
renderValueBox({
  valueBox(sum(as.numeric(as.character(subset(df_bar, df_bar$country_txt == input$Country)$nkill))), icon = "fas fa-skull", color = '#C23734')
})

```

### Total wounds

```{r}
renderValueBox({
  valueBox(sum(as.numeric(as.character(subset(df_bar, df_bar$country_txt == input$Country)$nwound))), icon = "fas fa-ambulance", color = '#F5980E')
})
```


Row {data-height=450}
-------------------------------------

### Deaths evolution

```{r}

renderPlotly({

t <- list(
  family = "helvetica",
  size = 12,
  color = 'white')

prueba <- data.frame(matrix(ncol = 3, nrow = 0))
colnames(prueba) = c('iyear', 'nkill', 'nwound')

iter = 1
esp = subset(df_bar, df_bar$country_txt == input$Country)
for (i in vector){
  dat = subset(esp, esp$iyear == i)
  num_kill = sum(as.numeric(as.character(dat$nkill)))
  num_her = sum(as.numeric(as.character(dat$nwound)))
  prueba[iter,] = c(i, num_kill, num_her)
  iter = iter + 1
}

plot_ly(prueba, x=~iyear, y=~as.numeric(as.character(nkill)), color = I('#C23734'), text = ~paste('Year: ', iyear, '<br>Deaths: ', as.numeric(as.character(nkill))),
    hoverinfo = "text") %>% add_lines() %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(title = ''),
    xaxis = list(title = 'Año'))
})

```

### Attack type deaths

```{r}

renderPlotly({
t <- list(
  family = "helvetica",
  size = 12,
  color = 'white')
dat = subset(df_bar, df_bar$country_txt == input$Country)

plot_ly(dat, x=~as.numeric(as.character(nkill)), y=~attacktype1, frame = ~iyear, color = I('#C23734'), showlegend = F, text = ~paste0(attacktype1, ': ',as.numeric(as.character(nkill))), hoverinfo = 'skip', textposition = 'outside', outsidetextfont = list(size=12, color = 'rgb(255,255,255)')) %>% animation_opts(frame = 800, redraw = F, transition = 800) %>% animation_slider(currentvalue = list(prefix = "YEAR ", font = list(color="white"))) %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(visible = F),
    xaxis = list(title = ''))
})
```

### Wounds evolution

```{r}
renderPlotly({

prueba <- data.frame(matrix(ncol = 3, nrow = 0))
colnames(prueba) = c('iyear', 'nkill', 'nwound')
t <- list(
  family = "helvetica",
  size = 12,
  color = 'white')

iter = 1
esp = subset(df_bar, df_bar$country_txt == input$Country)
for (i in vector){
  dat = subset(esp, esp$iyear == i)
  num_kill = sum(as.numeric(as.character(dat$nkill)))
  num_her = sum(as.numeric(as.character(dat$nwound)))
  prueba[iter,] = c(i, num_kill, num_her)
  iter = iter + 1
}
plot_ly(prueba, x=~iyear, y=~as.numeric(as.character(nwound)), color = I('#F5980E'), text = ~paste('Year: ', iyear, '<br>Wounds: ', as.numeric(as.character(nwound))),
    hoverinfo = "text") %>% add_lines() %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(title = ''),
    xaxis = list(title = 'Año'))
})
```


### Attack type wounds

```{r}

renderPlotly({
t <- list(
  family = "helvetica",
  size = 12,
  color = 'white')

dat = subset(df_bar, df_bar$country_txt == input$Country)

plot_ly(dat, x=~as.numeric(as.character(nwound)), y=~attacktype1, frame = ~iyear, color = I('#F5980E'), showlegend = F, text = ~paste0(attacktype1, ': ',as.numeric(as.character(nwound))) , textposition = 'outside', hoverinfo = 'skip', outsidetextfont = list(size=12, color = 'rgb(255,255,255)')) %>% animation_opts(frame = 800, redraw = F, transition = 800) %>% animation_slider(currentvalue = list(prefix = "YEAR ", font = list(color="white"))) %>% layout(paper_bgcolor='rgb(55,55,55)')  %>% 
          layout(plot_bgcolor='rgb(55,55,55)') %>% config(displayModeBar = FALSE) %>% layout(
    title = "",
    font = t,
    yaxis = list(visible = F),
    xaxis = list(title = ''))
})
```

